\section{Introduction}

In today’s fast-paced manufacturing environment, bottle factories are under constant pressure to produce pristine glass bottles in large volumes at high speeds, while not making a too big of an impact at the environment. The ever-growing demand for glass bottles \cite{ReturnableBottles} intensifies the challenges faced by these factories, requiring them to maintain efficiency without the cost of quality.  To manage external expectations, the factory must continuously monitor the production line, if they do that correctly they will be able to recognize defect bottles, such as broken and contaminated bottles.  Therefore the factory will find when a bottle is defect and might even why it is defect. Leading the factory to make better decisions for example recycle the broken bottles directly and clean the contaminated bottles to save both money and the environment.
\par
Traditionally, factories have a worker that stands beside the production line sometimes during parts of the day or the whole day. The worker manually visually inspect the bottles which not only cost a lot of money in salary but also will bottlenecks the whole production of bottles. A human can simply not keep track of the hundreds of bottles that the factory produces, humans are slow and error prone to this kind of work, while not mentioning how boring the work must be. Therefore this solution dose not satisfy the external expectations.  A different monitor solution must exist.
\par
Monitoring with cameras, by incorporating automated monitor systems in the production line, such as cameras. With the camera, the output feed can be used as input data in a machine learning algorithm. These algorithms has been trained to identify with high accuracy defect bottles. They can do that by analyzing the images from the camera therefore, acquiring the features of the bottle and then making a prediction on the status of the bottle if it is whole, broken or contaminated. If it is broken we can identify what kind of feature says it is broken which might lead the factory to why it is broken. Helping the factory to improve the production so less or none bottles are broken. 
\par
The approach of monitoring the production line with cameras offers a bunch of environmental and economical benefits. Broken bottles can be sent of to recycling that means the factory will reduce waste and help the environment, contaminated bottles can be cleaned and reused, saving the the factory  money. This surely sound as the best solution.
\par
This report will show the implementation of machine learning algorithms, evaluate the effectiveness of identifying defect bottles and also discuss the results of each algorithm. Additionally, mention limitations, challenges and ethical considerations of these technologies.
